\documentclass[a4paper,20pt]{article}

\title{\Huge \textbf{Certification Letter}}
\date{}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{times}
\usepackage{setspace}       %set space 

\geometry{left=1.5cm,right=1.5cm,top=1cm, bottom=1cm}
\begin{document}
\begin{spacing}{1.25}   
\maketitle

\LARGE \setlength\parindent{2em} This letter to certify that ZHANG, Wei from Feb. 17, 2016 to Jan. 8, 2017 worked with me as an affiliate at Lawrence Berkeley National Laboratory (LBNL), Berkeley, CA, USA. During the time he conducted independently research on the experimentation and testing of the digital readout in \emph{Topmetal-II$^-$} sensor under my supervision. 

\LARGE He completed a comprehensive study of the \emph{Topmetal-II$^-$} digital readout testing and got crediable data.  The results have been published at \emph{JINST} \textbf{12} C03004, 2017. The test platform remains at LBNL with me and Wei does not possess a replica. It prevents him from providing a live demonstration of his work. However I certify that all data and results that from the basis of his master thesis are genuine. 

\LARGE Please contact me should any questions arise.
\setlength\parskip{\baselineskip}

\noindent Sincerely yours,

\noindent Yuan Mei, Ph.D  

\noindent Staff Scientist,\\
\noindent Nuclear Science Division,\\
\noindent Lawrence Berkeley National Laboratory\\
\noindent 1 Cyclotron Road, M/S 88R0192\\
\noindent Berkeley, CA 94720\\
\noindent +1(510)486-7781\\
\end{spacing}
\end{document}
